Crystals

### 2017-02-13 doc/ms.tex
more work on that big table

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage{color}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}
\usepackage{natbib}
\usepackage{microtype}

@@

\begin{table}
\footnotesize
\centering
\begin{tabular}{|lll|}
\hline
{\bf Quantity}      &   {\bf Meaning}   &  {\bf Prior distribution}\\
\hline
{\em Prior information}&&\\
\hline
$n$ & Number of measurements & given\\
$\{\x_1, \x_2, ..., \x_n\}$  & $\x$-values of measurements & given \\
\hline
{\em Hyperparameters} & &\\
$N_{\rm narrow}$   &   Number of narrow spikes    &  $\propto 1/(N_{\rm narrow}+1)$, $N_{\rm narrow} \in \{0, 1, ..., 300\}$ \\
$N_{\rm wide}$   &   Number of wide spikes    &  $\propto 1/(N_{\rm wide}+1)$,
$N_{\rm wide} \in \{0, 1, ..., 300\}$ \\
$a_{\ln A, \rm narrow}$ & Typical log-amplitude of narrow spikes & Laplace(0, 5)\\
$a_{\ln A, \rm wide}$ & Typical log-amplitude of wide spikes & Laplace(0, 5)\\
$b_{\ln A, \rm narrow}$ & Diversity of log-amplitude of narrow spikes & Uniform(0, 5)\\
$b_{\ln A, \rm wide}$ & Diversity of log-amplitude of wide spikes & Uniform(0, 5)\\
$a_{\ln W, \rm narrow}$ & Typical log-width of narrow spikes & LogUniform$(10^{-3}x_{\rm range}, 0.05x_{\rm range})$\\
$a_{\ln W, \rm wide}$ & Typical log-width of wide spikes & LogUniform$(0.05x_{\rm range}, x_{\rm range})$\\
$b_{\ln W, \rm narrow}$ & Diversity of log-width of narrow spikes & Uniform(0, 0.1)\\
$b_{\ln W, \rm wide}$ & Diversity of log-width of wide spikes & Uniform(0, 0.2)\\
\hline
{\em Background parameters}&&\\
$b$       & Mean background level       & Laplace$(0, 5)$\\
$\{n_1, ..., n_4\}$  & Background deviations & iid Normal$(0,1)$\\
\hline 
{\em Noise parameters}&&\\
$\sigma_0$ &    Constant noise level  &   $\ln \sigma_0 \sim \textnormal{Laplace}(0,5)$\\
$\sigma_1$ &    Noise proportionality   &  $\ln \sigma_1 \sim \textnormal{Laplace}(0,5)$ \\
$\nu$     &   Shape parameter for residuals   &   LogUniform$(1, 1000)$\\
\hline
{\em Data}&&\\
\hline
$\{y_1, y_2, ..., y_n\}$  &   Measurements    & iid Student-$t(f(x_i; \params), ,\nu)$\\
\hline
\end{tabular}
\caption{\label{tab:priors}}
\end{table}

>>>>

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage{color}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{pdflscape}

@@

\begin{landscape}

\begin{table}
\footnotesize
\centering
\begin{tabular}{|lll|}
\hline
{\bf Quantity}      &   {\bf Meaning}   &  {\bf Prior distribution}\\
\hline
{\em Prior information}&&\\
\hline
$n$ & Number of measurements & given\\
$\{\x_1, \x_2, ..., \x_n\}$  & $\x$-values of measurements & given \\
\hline
{\em Hyperparameters} & &\\
$N_{\rm narrow}$   &   Number of narrow spikes    &  $\propto 1/(N_{\rm narrow}+1)$, $N_{\rm narrow} \in \{0, 1, ..., 300\}$ \\
$N_{\rm wide}$   &   Number of wide spikes    &  $\propto 1/(N_{\rm wide}+1)$,
$N_{\rm wide} \in \{0, 1, ..., 300\}$ \\
$a_{\ln A, \rm narrow}$ & Typical log-amplitude of narrow spikes & Laplace(0, 5)\\
$a_{\ln A, \rm wide}$ & Typical log-amplitude of wide spikes & Laplace(0, 5)\\
$b_{\ln A, \rm narrow}$ & Diversity of log-amplitude of narrow spikes & Uniform(0, 5)\\
$b_{\ln A, \rm wide}$ & Diversity of log-amplitude of wide spikes & Uniform(0, 5)\\
$a_{\ln W, \rm narrow}$ & Typical log-width of narrow spikes & LogUniform$(10^{-3}x_{\rm range}, 0.05x_{\rm range})$\\
$a_{\ln W, \rm wide}$ & Typical log-width of wide spikes & LogUniform$(0.05x_{\rm range}, x_{\rm range})$\\
$b_{\ln W, \rm narrow}$ & Diversity of log-width of narrow spikes & Uniform(0, 0.1)\\
$b_{\ln W, \rm wide}$ & Diversity of log-width of wide spikes & Uniform(0, 0.2)\\
\hline
{\em Background parameters}&&\\
$b$       & Mean background level       & Laplace$(0, 5)$\\
$\{n_1, ..., n_4\}$  & Background deviations & iid Normal$(0,1)$\\
\hline
{\em Narrow spike parameters}&&\\
$X_{i, \rm narrow}$ & Positions of narrow spikes &
                            Uniform$(x_{\rm min}, x_{\rm max})$ \\
$A_{i, \rm narrow}$ & Amplitudes of narrow spikes &
 $\ln A_{i, \rm narrow} \sim \textnormal{Laplace}\left(a_{\ln A, \rm narrow}, b_{\ln A, \rm narrow}\right)$ \\
$W_{i, \rm narrow}$ & Widths of narrow spikes &
 $\ln W_{i, \rm narrow} \sim \textnormal{Laplace}\left(a_{\ln W, \rm narrow}, b_{\ln W, \rm narrow}\right)$ \\
\hline
{\em Wide spike parameters}&&\\
$X_{i, \rm wide}$ & Positions of wide spikes &
          Uniform$(x_{\rm min}+0.3x_{\rm range}, x_{\rm max}-0.3x_{\rm range})$ \\
$A_{i, \rm wide}$ & Amplitudes of wide spikes &
 $\ln A_{i, \rm wide} \sim \textnormal{Laplace}\left(a_{\ln A, \rm wide}, b_{\ln A, \rm wide}\right)$ \\
$W_{i, \rm wide}$ & Widths of wide spikes &
 $\ln W_{i, \rm wide} \sim \textnormal{Laplace}\left(a_{\ln W, \rm wide}, b_{\ln W, \rm wide}\right)$ \\
\hline
{\em Noise parameters}&&\\
$\sigma_0$ &    Constant noise level  &   $\ln \sigma_0 \sim \textnormal{Laplace}(0,5)$\\
$\sigma_1$ &    Noise proportionality   &  $\ln \sigma_1 \sim \textnormal{Laplace}(0,5)$ \\
$\nu$     &   Shape parameter for residuals   &   LogUniform$(1, 1000)$\\
\hline
{\em Data}&&\\
\hline
$\{y_1, y_2, ..., y_n\}$  &   Measurements    & iid Student-$t(f(x_i; \params), ,\nu)$\\
\hline
\end{tabular}
\caption{\label{tab:priors}}
\end{table}

\end{landscape}
